Figures

### 2019-04-29 code/figures.rmd
Updated figures/tables after the switch to tetrachoric cors. for OR/RD

---
title: "Figures"
author: "Heterogeneity in direct replications in psychology and its association with effect size"
output: pdf_document
---

@@

```
Figure 1. Result of simulation relating $I^2$-values to between studies standard deviation. Each line represent one of 37 effects. Tau is not directly comparable across effect size measures.

@@

# save_plot("../figures/densities_het.png", densities,
#            nrow = 2,  base_width = 7, base_aspect_ratio = 0.618, dpi = 600)
```
Figure 2. Simulated $I^2$ (a) and $/tau^2$ (b) densities across 37 effects for zero, small, medium, and large heterogeneity according to the definitions of Higgins (2003), and a histogram of the observed I2 estimates for the 37 effects. For panel b) effects consist of correlations and biserial correlation and heterogeneity levels were approximated by Fisher’s z values corresponding to Higgins’ definitions for the median sample size of 108. Each simulated density consists of approximately 370,000 estimates.

@@

```{r cor_het_effect_size, results = "hide", cache=TRUE}
#Basic correlations
cor.test(res2$I2, res2$r) #pearson I2

I2_fit <- summary(lm(I2 ~ r, data = res2)) #for annotating figures

cor.test(res2$tau2, res2$r) #pearson tau2

tau2_fit <- summary(lm(tau2 ~ r, data = res2))

cor.test(res2$H2, res2$r) #pearson H2

H2_fit <- summary(lm(H2 ~ r, data = res2))

cor.test(res2$I2, res2$r, method = "spearman") #spearman

##Excluding anchoring effects
dropped_anchoring <- res2 %>%
  filter(!grepl("Anchoring", effect))

@@

bootfit <- boot(data=res2, statistic=pear, R=1000, formula= ~ r + I2)

@@

options(warn=-1)
bootfit <- boot(data=res2, statistic=spear, R=1000, formula= ~ r + I2)
options(warn=0)

@@

bootfit <- boot(data=res2, statistic=pear, R=1000, formula= ~ r + H2)

@@

I2 <- ggplot(res2, aes(x = r, y = I2)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = TRUE, color = "black") +
  coord_cartesian(ylim = c(0, 100)) +
  annotate("text", x = 0.14, y = Inf, vjust = 5, fontface = "italic", size = 3.5, label = paste0("b = ", format(round(I2_fit$coefficients[2, 1], 2), nsmall = 2), ", r = ", format(round(sqrt(I2_fit$r.squared), 2), nsmall = 2))) +
  theme_classic() +
  theme(axis.text.x = element_blank(), #drop x-axis labels in preparation for combining plots
        axis.ticks.x = element_blank(),
        panel.border = element_rect(fill = NA, colour = "black", #add box around plots
                                    size = 0.5, linetype = "solid")) +
  scale_y_continuous(name = expression(paste(italic(I)^2," index"))) +
  scale_x_continuous(name = NULL)

H2 <- ggplot(res2, aes(x = r, y = H2)) + 
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = TRUE, color = "black") +
  annotate("text", x = 0.14, y = Inf, vjust = 5, size = 3.5, fontface = "italic", label = paste("b = ", format(round(H2_fit$coefficients[2, 1], 2), nsmall = 2), ", r = ", format(round(sqrt(H2_fit$r.squared), 2), nsmall = 2))) +
  theme_classic() +
  theme(axis.text.x = element_blank(), #drop x-axis labels in preparation for combining plots
        axis.ticks.x = element_blank(),
        panel.border = element_rect(fill = NA, colour = "black", #add box around plots
                                    size = 0.5, linetype = "solid")) +
  scale_y_continuous(name = expression(paste(italic(H)^2," index", sep = ""))) +
  scale_x_continuous(name = NULL)

tau2 <- ggplot(res2, aes(x = r, y = tau2)) + 
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = TRUE, color = "black") +
  annotate("text", x = 0.14, y = Inf, vjust = 5, size = 3.5, fontface = "italic", label = paste("b = ", format(round(tau2_fit$coefficients[2, 1], 2), nsmall = 2), ", r = ", format(round(sqrt(tau2_fit$r.squared), 2), nsmall = 2))) +
  theme_classic() +
  theme(panel.border = element_rect(fill = NA, colour = "black", #add box around plots
                                    size = 0.5, linetype = "solid")) +
  scale_y_continuous(name = expression(paste(italic(tau)^2, " estimate"))) +
  scale_x_continuous(name = expression(paste("Biserial and Pearson's correlations ")))

@@

```
Figure 3. The correlation between a) I2 ,and effect size and b) H2 and c)  τ ̂^2and effect size for 37 effects from ten pre-registered multi-lab replication projects. Shaded bands represent 95% confidence intervals

>>>>

---
title: "Figures"
author: "Heterogeneity in direct replications in psychology and its association with effect size"
output: 
  pdf_document: 
    latex_engine: xelatex
---

@@

Figure 1. Result of simulation relating $I^2$-values to between studies standard deviation. Each line represent one of 37 effects. Tau is not directly comparable across effect size measures.

@@

# save_plot("../figures/densities_het.png", densities,
#            nrow = 2,  base_width = 7, base_aspect_ratio = 0.618, dpi = 600)
```

Figure 2. Simulated $I^2$ (a) and $/tau^2$ (b) densities across 37 effects for zero, small, medium, and large heterogeneity according to the definitions of Higgins (2003), and a histogram of the observed I2 estimates for the 37 effects. For panel b) effects consist of correlations and biserial correlation and heterogeneity levels were approximated by Fisher’s z values corresponding to Higgins’ definitions for the median sample size of 108. Each simulated density consists of approximately 370,000 estimates.

@@

```{r cor_het_effect_size, results = "hide", cache=TRUE}
#Basic correlations
cor.test(res$I2, res$r) #pearson I2

I2_fit <- summary(lm(I2 ~ r, data = res)) #for annotating figures

cor.test(res$tau2, res$r) #pearson tau2

tau2_fit <- summary(lm(tau2 ~ r, data = res))

cor.test(res$H2, res$r) #pearson H2

H2_fit <- summary(lm(H2 ~ r, data = res))

cor.test(res$I2, res$r, method = "spearman") #spearman

##Excluding anchoring effects
dropped_anchoring <- res %>%
  filter(!grepl("Anchoring", effect))

@@

bootfit <- boot(data=res, statistic=pear, R=1000, formula= ~ r + I2)

@@

options(warn=-1)
bootfit <- boot(data=res, statistic=spear, R=1000, formula= ~ r + I2)
options(warn=0)

@@

bootfit <- boot(data=res, statistic=pear, R=1000, formula= ~ r + H2)

@@

I2 <- ggplot(res, aes(x = r, y = I2)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = TRUE, color = "black") +
  coord_cartesian(ylim = c(0, 100)) +
  annotate("text", x = 0.14, y = Inf, vjust = 5, fontface = "italic", size = 3.5, label = paste0("b = ", format(round(I2_fit$coefficients[2, 1], 2), nsmall = 2), ", r = ", format(round(sqrt(I2_fit$r.squared), 2), nsmall = 2))) +
  theme_classic() +
  theme(axis.text.x = element_blank(), #drop x-axis labels in preparation for combining plots
        axis.ticks.x = element_blank(),
        panel.border = element_rect(fill = NA, colour = "black", #add box around plots
                                    size = 0.5, linetype = "solid")) +
  scale_y_continuous(name = expression(paste(italic(I)^2," index"))) +
  scale_x_continuous(name = NULL)

H2 <- ggplot(res, aes(x = r, y = H2)) + 
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = TRUE, color = "black") +
  annotate("text", x = 0.14, y = Inf, vjust = 5, size = 3.5, fontface = "italic", label = paste("b = ", format(round(H2_fit$coefficients[2, 1], 2), nsmall = 2), ", r = ", format(round(sqrt(H2_fit$r.squared), 2), nsmall = 2))) +
  theme_classic() +
  theme(axis.text.x = element_blank(), #drop x-axis labels in preparation for combining plots
        axis.ticks.x = element_blank(),
        panel.border = element_rect(fill = NA, colour = "black", #add box around plots
                                    size = 0.5, linetype = "solid")) +
  scale_y_continuous(name = expression(paste(italic(H)^2," index", sep = ""))) +
  scale_x_continuous(name = NULL)

tau2 <- ggplot(res, aes(x = r, y = tau2)) + 
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = TRUE, color = "black") +
  annotate("text", x = 0.14, y = Inf, vjust = 5, size = 3.5, fontface = "italic", label = paste("b = ", format(round(tau2_fit$coefficients[2, 1], 2), nsmall = 2), ", r = ", format(round(sqrt(tau2_fit$r.squared), 2), nsmall = 2))) +
  theme_classic() +
  theme(panel.border = element_rect(fill = NA, colour = "black", #add box around plots
                                    size = 0.5, linetype = "solid")) +
  scale_y_continuous(name = expression(paste(italic(tau)^2, " estimate"))) +
  scale_x_continuous(name = expression(paste("Biserial and Pearson's correlations ")))

@@

Figure 3. The correlation between a) I2 ,and effect size and b) H2 and c)  τ ̂^2and effect size for 37 effects from ten pre-registered multi-lab replication projects. Shaded bands represent 95% confidence intervals
